Prefix-free graphs and suffix array construction in sublinear space

### 2023-08-10 manuscript/content/03_sa_construction.tex
last read done, submiting...

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{images/ids_and_positions.png}
    \caption{
    Segment join of segments from the running example, corresponding segment IDs, and positions. Permuting IDs and positions according to the \texttt{ISA} results in the segment ID array \texttt{ID} and the segment position array \texttt{pos} shown in Table \ref{tab:suffix}. \label{fig:ids_and_positions}
    }
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{images/ids_and_positions.png}
    \caption{
        Segment join of segments from the running example, corresponding segment IDs, and positions. Permuting IDs and positions according to the \texttt{ISA} results in the segment ID array \texttt{(ID)} and the segment position array \texttt{(pos)} shown in Table \ref{tab:suffix}. \label{fig:ids_and_positions}
    }
\end{figure}
